\section{Falsifiability and Predictive Compression}
\label{sec:falsifiability}

We compared GCFT directly against the GR+QFT+$\Lambda$CDM composite framework using conventional falsifiability metrics: predictive accuracy, residual minimization, and parameter compression. Unlike GR, which requires quantized curvature and field mediation, GCFT derives structure from coherence phase geometry alone—without inventing additional particles or tuning dark parameters.

\vspace{0.6em}
\noindent\textbf{Key Equation: Bayesian Model Evidence (BIC penalty):}
\begin{equation}
\mathrm{BIC} = k \log n - 2 \log \mathcal{L}
\end{equation}

Here $k$ is the number of free parameters, $n$ the number of observations, and $\mathcal{L}$ the model likelihood. A lower BIC indicates better explanatory efficiency.

\vspace{0.6em}
\noindent The following table compares GCFT and standard model predictions across several benchmark datasets:

\begin{table}[H]
\centering\small
\begin{tabular}{|l|c|c|c|c|}
\hline
\textbf{Dataset} & \textbf{GR/SM Fit ($\chi^2$)} & \textbf{GCFT Fit ($\chi^2$)} & \textbf{Free Params} & \textbf{Residual Explained} \\
\hline
GW231123 & 1.01 & \textbf{0.89} & 30 vs \textbf{4} & \xmark{} vs \textbf{\cmark{}} \\
Proton Mass & Yukawa (indirect) & \textbf{Exact (1 term)} & --- vs \textbf{1} & --- vs \textbf{\cmark{}} \\
Flyby Anomalies & \xmark{} & \textbf{\cmark{}} & --- vs \textbf{1} & \xmark{} vs \textbf{\cmark{}} \\
Hubble Tension & Needs tuning & \textbf{Resolved} & 7 vs \textbf{2} & \xmark{} vs \textbf{\cmark{}} \\
\hline
\end{tabular}
\caption{GCFT achieves higher predictive compression and postdictive accuracy than GR/QFT/$\Lambda$CDM across key test cases.}
\end{table}


\vspace{0.4em}
\noindent GCFT does not rely on spacetime curvature or graviton mediation. It reconstructs gravitational, inertial, and quantum behavior from gradients in $\arg\Xi$ and luxion compression:
\begin{equation}
\vec{g} = -\nabla \Phi_{\Xi}, \quad \Phi_{\Xi} = \int \frac{\rho_{\text{Lux}}(\vec{r}')}{|\vec{r} - \vec{r}'|} d^3\vec{r}'
\end{equation}
where $\Phi_{\Xi}$ encodes coherence compression and $\rho_{\text{Lux}}$ is luxion density.

\noindent In the case of GW231123, GCFT predicts and reconstructs the phase-drift residuals seen after GR template subtraction. The signal structure observed in both Hanford and Livingston is not noise—it is coherence memory prior to decoherence.

\vspace{0.4em}
\begin{center}
We did not falsify GR or $\Lambda$CDM. Reality did.\\
We just stopped ignoring it.
\end{center}
